\documentclass{article}
\usepackage[utf8]{inputenc}

\title{PS5 Hoehne}
\author{Jordan Hoehne }
\date{February 20th 2018}

\usepackage{natbib}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[numbers]{natbib}
\begin{document}

\maketitle

\section{Non-API Data}
The data source I chose for my Non-API data is the IMDb page for the movies at the Warren theater. The Warren theater is the best theater closest to Norman. I want to explore all of the features of the data. I used a tutorial from YouTube to help me walk through the syntax of the problem, https://goo.gl/YTFVJ2. I also, used NewEgg, a popular computer and computer parts company to pull GPU availability from their website to see which GPU's are available, which then creates a csv. file with the output. If I had more time, I would have liked to pull the prices for each product.


\section{API Data}
The data I wanted to explore for my API data was Twitter. I have previously worked with web scrapping in JavaScript, but I coded this project in Python. Accessing the keys was similar, however instead of scanning tweets I wanted to pull user information. I pulled data on the followers of an account which could be useful in building an application to measure response and temperament to tweets helping a user identify successful tweeting strategies. I used this video on YouTube as a resource for this project. https://goo.gl/dopvq8. I also tweeted you from my account and left the code in there as a plus. I would like to work with the API for my mining rigs to compile a file on my mining rig data to measure productivity. This would help me identify trends and track payouts as well as other data.

\centering

\end{document}
